\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-04-28 paper.qmd
Add binning data dist

Number of bins is set by fixing $b_1$, which determines the binwidth accounting the offset $q_1$ and breaks on $x_1$, is calculated as

$$
a_1 = \frac{r_1 + q_1}{b_1}.
$$

The computed binwidth then determines the number of vertical bins, $b_2$, and vertical binwidth, which are computed based on $r_2$, the offset $q_2$, and the height/width ratio of a regular hexagon, $\frac{2}{\sqrt{3}}$ as

$$
a_2 = \frac{r_2 + q_2}{0.75 \times b_2}.
$$

@@

Points are allocated to the bin that they fall in. XXX How are you doing this? Do you check the bounds of the hexagon? Or do you use distance to centroid?

>>>>

The value for $b_2$ is computed by fixing $b_1$.

<!-- Number of bins is set by fixing $b_1$, which determines the binwidth accounting the offset $q_1$ and breaks on $x_1$, is calculated as  -->

<!-- $$ -->
<!-- a_1 = \frac{r_1 + q_1}{b_1}. -->
<!-- $$ -->

<!-- The computed binwidth then determines the number of vertical bins, $b_2$, and vertical binwidth, which are computed based on $r_2$, the offset $q_2$, and the height/width ratio of a regular hexagon, $\frac{2}{\sqrt{3}}$ as -->

<!-- $$ -->
<!-- a_2 = \frac{r_2 + q_2}{0.75 \times b_2}. -->
<!-- $$ -->

@@

Points are allocated to the bin that they fall in by considering the nearest nearest centroid.

<!-- XXX How are you doing this? Do you check the bounds of the hexagon? Or do you use distance to centroid? -->

### 2024-04-28 paper.tex
Add binning data dist

Number of bins is set by fixing \(b_1\), which determines the binwidth
accounting the offset \(q_1\) and breaks on \(x_1\), is calculated as

\[
a_1 = \frac{r_1 + q_1}{b_1}.
\]

The computed binwidth then determines the number of vertical bins,
\(b_2\), and vertical binwidth, which are computed based on \(r_2\), the
offset \(q_2\), and the height/width ratio of a regular hexagon,
\(\frac{2}{\sqrt{3}}\) as

\[
a_2 = \frac{r_2 + q_2}{0.75 \times b_2}.
\]

@@

Points are allocated to the bin that they fall in. XXX How are you doing
this? Do you check the bounds of the hexagon? Or do you use distance to
centroid?

>>>>

The value for \(b_2\) is computed by fixing \(b_1\).

@@

Points are allocated to the bin that they fall in by considering the
nearest nearest centroid.
